Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-05-30 WRITEUP/ms.tex

\begin{abstract}
We study the properties of molecular cloud complexes (MCCs) using cosmological zoom-in simulation of a
$z\simeq 6$ prototypical galaxy (``\flower'').
%
We identify MCCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter
to \obs.
%
In \flower, the typical MCC mass is $10^{6.5}$\,\Msun, with sizes $R\lesssim100$\,pc.
%
We identify gravitationally unstable MCCs both via Toomre $Q_{\rm eff}$ analysis and
the more observationally accessible virial parameter ($\alpha_{\rm vir}$) analysis.
MCCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of
instability to % gravitational
collapse.
%
Their velocity dispersion and gas surface density are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
%
We show that large-scale rotation is an important contributor to the velocity dispersion of some MCCs.
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) on
$\lesssim$40\,pc are necessary to shed light on the star-forming gas dynamics since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

From the dispersion relation, a parameter $Q$ can be derived such that $Q < 1$ when instability occurs, that reproduces this inequality to order unity. For a collisionless fluid---such as an ensemble of stars--- this parameter is \citep{Toomre64a}
\begin{equation}
Q_{\star} \equiv\frac{\sigma_{\star}\kappa}{3.36 G \Sigma_{\star}}\,.
\end{equation}
The equivalent parameter for a collisional gas was derived by \citet{Goldreich65a}
\begin{equation}
Q_{\rm gas}\equiv\frac{\sigma_{\rm gas}\kappa}{\pi G \Sigma_{\rm gas}}\,.
\label{eqn:Q}
\end{equation}
In the thin disk approximation ($kh\ll1$), instability ($\omega^2 < 0$ in  \Eq{3Ddisp}) occurs on scales $k$ such that $Q < Q_{\rm crit}\simeq1$ (or equivalently $\omega^2 < 0$). A frequently used observable proxy for $Q$ is the ratio of disk circular velocity to root-mean-square velocity dispersion $v_{\rm circ}/\sigma_{\rm disk}$ \citep[e.g.,][]{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}.
% https://ned.ipac.caltech.edu/level5/March15/Glazebrook/Glazebrook5.html
%

@@

The simulation zooms in on a galaxy named after the flower \flower whose properties are given in \citet{Pallottini17a} and are briefly summarized in the following. \flower is a Lyman-break galaxy that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. \flower has a stellar mass of $M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne.
%
The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$ relation observed at high redshift \citep{Jiang16a}, which is higher than normal local galaxies. The effective stellar radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
\caption{
    {\it Top}: Star formation history of \flower. {\it Bottom}:
    projected stellar mass distribution during {\it (a)} an early
    accreting phase;  {\it (b)} a major starburst following a merger
    event; and {\it (c)} a relatively quiescent post-starburst
    phase.
\label{fig:SFH}}
\end{figure*}

One of the main advantages of studying galaxies in simulations is that we can examine how their dynamical properties evolve with time, which
is interesting in order to understand the physical processes that determine the morphology and dynamical properties of galaxies, which in turn affect their \SF.
%
%This is advantageous especially at early cosmic epochs, when the densest structures are beginning to form; gas is constantly being accreted onto the central galaxy from the cosmic web and satellite galaxies, thereby leading to bursts of \SF. Meanwhile, tidal forces resulting from interactions with these surrounding galaxies can disrupt the main disk and arms, likely leading to different dynamical states for the molecular structures compared to more evolved galaxies found at a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive ones). % mainly expecting differences in alpha_vir, sigma, M_cl.
%mm [delete para break]
The \SF history\footnote{Note that here the SFR is calculated based on the stellar mass formed in the last 4 Myr within 3.5 kpc from the galaxy center of mass. The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher since there the SFR accounts for the contribution from massive satellite galaxies within the virial radius ($\approx$15\,kpc).} of \flower is shown in \Fig{SFH}. The SFR of \flower varies between $\sim$30--80 \Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\approx 700$ Myr.

Given the stochastic nature of \flower in its star formation history, we mostly focus on few of its most extreme evolutionary stages in this work (see \Sec{singless}).
%
These phases correspond to (a) an intensely accreting phase and (b) a starburst phase (\Fig{SFH}). We are interested in determining whether MCC properties are sensitive to these different dynamical conditions. For completeness, we also show the scaling relations examined for the other evolutionary stages traced in the simulation (see \Sec{ncut}).

In \Sec{rot}, we investigate the importance of rotation support from large-scale motions in the MCC dynamics by comparing their properties
in the disturbed phase of \flower and in the disk-like ordered phase.

Throughout this paper, we describe the dense gas regions outside the main disk of \flower as satellite galaxies. The distinction between clumps and satellites is admittedly somewhat ambiguous, though, and we consider it only as a working one.

\AF{To be discussed at the end}

@@

In the clump-finding process (in position-position-position space; PPP), we employ a set of different density thresholds defined based on the molecular hydrogen density of \flower at different evolutionary stages ($z=6.0$--7.2).
%
We note that this process is the three-dimensional analog to identifying molecular structures based on the noise levels in position-position-velocity (PPV) maps that observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN. This is commonly done by
identifying clumps based on/after applying S/N-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a}).
%
%We note that, owing to the nature of \obs, such structures are identified in position-position-velocity (PPV) space, whereas in simulations, one has the full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
Existing studies find a good correspondence in the dynamical properties extracted in PPV- versus PPP-space for well-isolated structures (\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, Pan15a}, but see \citealt{Ballesteros-Paredes02a} and \citealt{Shetty10a} for a discussion on caveats and limitations).
% large scale structure in PPP may be identified as numerous lower mass structures in the PPV cube due to gradients in the LOS and conversly, superposition when spatially distinct components with the same velocity are "merged" into one component in the PPV space when observed along the LOS (see Fig. 1 of Beaumount13a). (may be worth putting more thoughts on this after the report is due).

@@

The most massive ($M_{\rm gas}>$10$^7$\,\Msun) cloud corresponds to the molecular disk of the galaxy (see e.g., \Fig{MCC}), 
which is identified as a single component at low $n_{\rm cut}$. This main disk component occupy the top right corner of \Fig{stellarRatio16}, with a \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} 
stellar-to-gas mass ratio of $\simeq$\,50--100. 
Such structure has velocity dispersion dominated by bulk motions, as shown in \Fig{vv}, where we compare 
the velocity dispersions of MCCs  
resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) 
for the accreting and quiescent phases of \flower.
The accreting phase (\Fig{MCC}) of \flower displays a disturbed morphology compared to the
quiescent phase, which displays a disk-like morphology (\Fig{MCC28}).
Excluding the molecular disk, the velocity dispersions of most MCCs in the accreting phase of \flower 
are dominated by turbulent motions. 
On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs
in the quiescent disk-like phase.

@@

\begin{figure}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-sigma-kms-bulk_sigma-kms-NT} \\
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss28-sigma-kms-bulk_sigma-kms-NT}
\caption{Gas velocity dispersions from bulk motions and turbulent motions for MCCs identified in accreting (top) and
quiescent phase (bottom) of \flower across all $n_{\rm cut}$ (same color-coding as \Fig{stellarRatio16}).
The accreting phase (\Fig{MCC}) of \flower displays a more disturbed morphology compared to the
quiescent phase, which displays a disk-like morphology (\Fig{MCC28}).
Velocity dispersion from turbulent motions dominates over bulk motions for most MCCs in the accreting phase. 
On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs
in the quiescent disk-like phase.
\label{fig:vv}}
\vspace{0.5em}
\end{figure}

The local sound speed of all identified molecular complexes is typically much smaller than their non-thermal (turbulent) velocities,
as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e. $c_s^2 \ll \sigma_{\rm NT}^2$. In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
\caption{Same as \Fig{larsons_single}, except star symbols are showing MCCs identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages (see colorbar). Left panels show MCCs identified using a low density threshold of $n_{\rm cut}$\eq0.53\,\cc and right panels show MCCs
identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
The biggest MCCs identified at lowest density threshold, occupying the top right corner of the top left panel), are broken into smaller MCCs at higher
density thresholds (top right panel).
\label{fig:alpha16-28}}
\end{figure*}

@@

% middle
While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some of them (see \Fig{stellarRatio16}).
% 
MCCs with the highest \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of \Fig{MCC} and \Fig{MCC28}, see also \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower. This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability of such MCCs.

% PVE
Motivated by observational studies, we also plot the $\sigma_{\rm gas}^2/R$ ratio and gas surface density of MCCs in the bottom left panels of \Fig{larsons_single}. In the same plot, we show those observed in the Galactic Ring Survey (GRS) of the Milky Way \citep{Heyer09a} for comparison. Dashed lines in the figure show the loci along which the annotated external pressures are needed for any molecular clouds in equilibrium to have certain linewidths for a given set of surface densities (see \Sec{PVE}). 
At a given gas surface density, MCCs display a range of $\sigma^2/R$. 
Such variations in $\sigma^2/R$ is observed in GMCs of the Milky Way \citep{Heyer09a}.

If constant column density (Larson's third law) is truly a fundamental properties of molecular clouds, 
% or the roughly linear relationship between $\rho$ and $R$ of MCCs.
one would expect a single point in the $\sigma_{\rm gas}^2/R$--$\Sigma$ relation at a given gas mass surface density $\Sigma$.
The variation in $\sigma^2/R$ with $\Sigma$ seen here suggests that column density is not a fundamental properties of 
molecular clouds. Previous studies suggest that the observed mass-size relation of molecular clouds 
is solely a result of $\rho\propto M R^{-3}$ and may be an artifact of the limited range of 
column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}.
%For instance, \citet{Ballesteros02a} show that the density
%of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
%two-dimensional space; the latter is done in \obs.
%When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
%line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
%They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
%observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
%observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
%% since $M$ would then scale as $R^{3}$ (ånd naturally display a linear relationship in $\log M - \log R$ plot).

@@

% Starburst
In the starburst phase, MCCs have similar velocity dispersion and sizes as those in the accreting phase; however, 
MCCs in the starburst phase span a wider range in gas surface density 
(bottom panels of \Fig{larsons_single}) and have lower virial parameters, even
for MCCs with masses $<$\,10$^7$\,\Msun (i.e., excluding the molecular disk of \flower identified).
That is, more MCCs in the starburst phase of \flower are more susceptible to collapse, as expected.
%
% Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase.
%\Fig{alphaEvol} shows that most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
%the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
%This is consistent with our physical intuition of gas instability leading to \SF.

@@

In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
%%
%We exclude the biggest MCC identified in each evolutionary stage, which correspond to the main disk of \flower (i.e., the top right cluster of points in the linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}).
The MCCs of \flower have dynamics largely similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity dispersions of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms.
%
Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the locus of $\sigma_{\rm gas}\propto R^{0.56}$. Such high velocity dispersion is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}). In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.

>>>>

\begin{abstract}
We study the properties of molecular cloud complexes (MCCs) using cosmological zoom-in simulation of a
$z\simeq 6$ prototypical galaxy (``\flower'').
%
We identify MCCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter
to \obs.
%
In \flower, the typical MCC mass is $10^{6.5}$\,\Msun, with sizes $R\lesssim100$\,pc, comparable to nearby spirals and starburst galaxies.
%
We identify gravitationally unstable MCCs both via Toomre $Q_{\rm eff}$ analysis and
the more observationally accessible virial parameter ($\alpha_{\rm vir}$) analysis.
MCCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of
instability to % gravitational
collapse.
%
Their velocity dispersion and gas surface density are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
%
We show that large-scale rotation is an important contributor to the velocity dispersion of some MCCs.
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) on
$\lesssim$40\,pc are necessary to shed light on the star-forming gas dynamics since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

From the dispersion relation, a parameter $Q$ can be derived such that $Q < 1$ when instability occurs, that reproduces this inequality to order unity. For a collisionless fluid---such as an ensemble of stars--- this parameter is \citep{Toomre64a}
\begin{equation}
Q_{\star} \equiv\frac{\sigma_{\star}\kappa}{3.36 G \Sigma_{\star}}\,.
\end{equation}
The equivalent parameter for a collisional gas was derived by \citet{Goldreich65a}
\begin{equation}
Q_{\rm gas}\equiv\frac{\sigma_{\rm gas}\kappa}{\pi G \Sigma_{\rm gas}}\,.
\label{eqn:Q}
\end{equation}
In the thin disk approximation ($kh\ll1$), instability occurs on scales $k$ such that $Q < Q_{\rm crit}\simeq1$ (or equivalently $\omega^2 < 0$ in \Eq{3Ddisp}). A frequently used observable proxy for $Q$ is the ratio of disk circular velocity to root-mean-square velocity dispersion $v_{\rm circ}/\sigma_{\rm disk}$ \citep[e.g.,][]{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}.
% https://ned.ipac.caltech.edu/level5/March15/Glazebrook/Glazebrook5.html
%

@@

The simulation zooms in on a galaxy named after the flower \flower whose properties are given in \citet{Pallottini17a} and are briefly summarized in the following. \flower is a Lyman-break galaxy that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. \flower has a stellar mass of $M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne.
%
The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$ relation observed at high redshift \citep{Jiang16a}. The effective stellar radius of \flower is $\simeq$\,0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.

@@

\begin{figure*}[hptb]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
\caption{
    {\it Top}: Star formation history of \flower. {\it Bottom}:
    projected stellar mass distribution during {\it (a)} an early
    accreting phase;  {\it (b)} a major starburst following a merger
    event; and {\it (c)} a relatively quiescent post-starburst
    phase.
\label{fig:SFH}}
\end{figure*}

One of the main advantages of studying galaxies in simulations is that we can examine how their dynamical properties evolve with time, which
is interesting in order to understand the physical processes that determine the morphology and dynamical properties of galaxies, which in turn affect their \SF.
%
%This is advantageous especially at early cosmic epochs, when the densest structures are beginning to form; gas is constantly being accreted onto the central galaxy from the cosmic web and \section{•}
atellite galaxies, thereby leading to bursts of \SF. Meanwhile, tidal forces resulting from interactions with these surrounding galaxies can disrupt the main disk and arms, likely leading to different dynamical states for the molecular structures compared to more evolved galaxies found at a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive ones). % mainly expecting differences in alpha_vir, sigma, M_cl.
%mm [delete para break]
The \SF history\footnote{Note that here the SFR is calculated based on the stellar mass formed in the last 4 Myr within 3.5 kpc from the galaxy center of mass. The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher since there the SFR accounts for the contribution from massive satellite galaxies within the virial radius ($\approx$15\,kpc).} of \flower is shown in \Fig{SFH}. The SFR of \flower varies between $\sim$30--80 \Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\approx 700$\,Myr.

Given the stochastic nature of \flower in its star formation history, we mostly focus on few of its most extreme evolutionary stages in this work (see \Sec{singless}).
%
These phases correspond to (a) an intensely accreting phase and (b) a starburst phase (\Fig{SFH}). We are interested in determining whether MCC properties are sensitive to these different dynamical conditions. For completeness, we also show the scaling relations examined for the other evolutionary stages traced in the simulation (see \Sec{ncut}).
In \Sec{dist}, we show the importance of rotation support from large-scale motions in the MCC dynamics 
by comparing their properties in the disturbed phase of \flower and in the disk-like ordered phase.

@@

In the clump-finding process (in position-position-position space; PPP), we employ a set of different density thresholds defined based on the molecular hydrogen density of \flower at different evolutionary stages ($z=6.0$--7.2).
%
We note that this process is the three-dimensional analog to identifying molecular structures based on the noise levels in position-position-velocity (PPV) maps that observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN. This is commonly done by
identifying clumps based on/after applying S/N-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; e.g., \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a, DonovanMyer13a}).
%
%We note that, owing to the nature of \obs, such structures are identified in position-position-velocity (PPV) space, whereas in simulations, one has the full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
Existing studies find a good correspondence in the dynamical properties extracted in PPV- versus PPP-space for well-isolated structures (\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, Pan15a}, but see \citealt{Ballesteros-Paredes02a} and \citealt{Shetty10a} for a discussion on caveats and limitations).
% large scale structure in PPP may be identified as numerous lower mass structures in the PPV cube due to gradients in the LOS and conversly, superposition when spatially distinct components with the same velocity are "merged" into one component in the PPV space when observed along the LOS (see Fig. 1 of Beaumount13a). (may be worth putting more thoughts on this after the report is due).

@@

The most massive ($M_{\rm gas}>$10$^7$\,\Msun) cloud corresponds to the molecular disk of the galaxy (see e.g., \Fig{MCC}), 
which is identified as a single component at low $n_{\rm cut}$. This main disk component occupy the top right corner of \Fig{stellarRatio16}, with a \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} 
stellar-to-gas mass ratio of $\simeq$\,50--100. 
The velocity dispersion of such structure is dominated by bulk motions, as shown in \Fig{vv}, where we compare 
the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) 
in the accreting and quiescent phases of \flower.
The accreting phase of \flower displays a disturbed morphology (\Fig{MCC}) while the 
quiescent phase displays a disk-like morphology (\Fig{MCC28}).
Excluding the structure corresponding to the molecular disk, the 
velocity dispersions of most MCCs in the accreting phase of \flower are dominated by turbulent motions.
On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs
in the quiescent disk-like phase.

@@

\begin{figure}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-sigma-kms-bulk_sigma-kms-NT} \\
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss28-sigma-kms-bulk_sigma-kms-NT}
\caption{Gas velocity dispersions resulting from bulk versus turbulent motions 
for MCCs identified across all $n_{\rm cut}$ (same color-coding as \Fig{stellarRatio16}) in the accreting (top) and
quiescent phase (bottom) of \flower.
The accreting phase (\Fig{MCC}) of \flower displays a more disturbed morphology compared to the
quiescent phase, which displays a disk-like morphology (\Fig{MCC28}).
Velocity dispersion from turbulent motions dominates over bulk motions for most MCCs in the accreting phase. 
On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs
in the quiescent disk-like phase.
\label{fig:vv}}
\vspace{0.5em}
\end{figure}

The local sound speed of all molecular complexes identified is typically much smaller than their non-thermal (turbulent) velocities,
as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e., $c_s^2 \ll \sigma_{\rm NT}^2$. In particular, the average Mach number for MCCs identified at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
\caption{Same as \Fig{larsons_single}, except star symbols are showing MCCs identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages (see colorbar). Left panels show MCCs identified using a low density threshold of $n_{\rm cut}$\eq0.53\,\cc and right panels show MCCs
identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
The biggest MCCs identified at lowest density thresholds, occupying the top right corner of the top left panel, correspond to the molecular 
disk and arms of \flower, and are broken down into smaller MCCs at higher density thresholds (see top right panel).
\label{fig:alpha16-28}}
\end{figure*}

@@

% middle
While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some of them (see \Fig{stellarRatio16}).
% 
The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio 
($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Fig{MCC28}, and \Sec{distribution}). A large fraction of stellar mass is already assembled in \flower in such MCC, which explains the low total virial parameter seen in the most massive MCC of \flower in this phase, as shown in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability of such MCCs. On the other hand, the 
remaining MCCs in this phase are stable, with virial parameter comparable to some of the molecular structures observed in the Milky Way
but the former is more massive.

% PVE
Motivated by observational studies, we also plot the $\sigma_{\rm gas}^2/R$ ratio and gas surface density of MCCs in the accreting phase of \flower in the bottom left panels of \Fig{larsons_single}. In the same plot, we show those observed in the Galactic Ring Survey (GRS) of the Milky Way \citep{Heyer09a} for comparison. Dashed lines in the figure show the loci along which the annotated external pressures are needed for any molecular clouds in equilibrium to have certain linewidths for a given set of surface densities (see \Sec{PVE}). 
At a given gas surface density, MCCs display a range of $\sigma^2/R$. 
Such variation in $\sigma^2/R$ is observed in GMCs in the central and outer part of the Milky Way \citep{Oka01a, Heyer09a}.

If constant column density (Larson's third law) is truly a fundamental properties of molecular clouds % or the roughly linear relationship between $\rho$ and $R$ of MCCs.
(i.e., if virialization is a universal property of molecular clouds with negligible surface pressure), 
one would expect a single point in the $\sigma_{\rm gas}^2/R$--$\Sigma$ relation at a given gas mass surface density $\Sigma$. 
The variation in $\sigma^2/R$ with $\Sigma$ seen here suggests that column density is not a fundamental properties of 
molecular clouds. Previous studies suggest that the observed mass-size relation of molecular clouds 
is solely a result of $\rho\propto M R^{-3}$ and may be an artifact of the limited range of 
column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}.
%For instance, \citet{Ballesteros02a} show that the density
%of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
%two-dimensional space; the latter is done in \obs.
%When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
%line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
%They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
%observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
%observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
%% since $M$ would then scale as $R^{3}$ (ånd naturally display a linear relationship in $\log M - \log R$ plot).

@@

% Starburst
In the starburst phase, MCCs have velocity dispersion and sizes similar to those in the accreting phase; however, 
MCCs in the starburst phase span a wider range in gas surface density 
(bottom panels of \Fig{larsons_single}) and have lower virial parameters, even
for MCCs with masses $<$\,10$^7$\,\Msun (i.e., excluding the molecular disk of \flower identified).
That is, more MCCs in the starburst phase of \flower are more susceptible to collapse, as expected.
The gas surface density of MCCs in both accreting and starburst phases is higher than the Milky Way at 8\,kpc, but comparable to 
those observed in starburst galaxies and the nearby ULIRGs \citep{Boulares90a, Scoville91a, Weiss01a, Leroy15a}.
% M82: 0.1 g cm^-2
% Arp 220: 7-20 g cm^-2
%
% Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase.
%\Fig{alphaEvol} shows that most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
%the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
%This is consistent with our physical intuition of gas instability leading to \SF.

@@

In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
%%
%We exclude the biggest MCC identified in each evolutionary stage, which correspond to the main disk of \flower (i.e., the top right cluster of points in the linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}).
The MCCs of \flower have dynamics largely similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity dispersions of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms.
%
Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lies along the locus of $\sigma_{\rm gas}\propto R^{0.56}$. Such high velocity dispersion of MCCs in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}). In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
